MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-09-17 MAESTROeX_I/results.tex
enlarged font in fig 3.  and also enlarged fig 3 itself
figure size
other figure sizes

\subsection{Performance and Scaling}\label{sec:scaling}
We perform weak scaling tests for simulations of convection preceding ignition in a spherical, full-star Chandrasekhar mass white dwarf. 
The simulation setup remains the same as reported in Section 3 of \cite{MAESTRO_AMR} and originally used in \cite{MAESTRO_convection}, and thus we emphasize that these scaling tests are performed using meaningful, scientific calculations.
Here, we perform simulations using $256^3, 512^3, 768^3, 1024^3, 1280^3$, and $1536^3$ grid cells on a spatially uniform grid (no AMR).
We divide each simulation into $64^3$ grids, so these simulations contain between 64 grids ($256^3$) and 13,824 grids ($1536^3$).
These simulations were performed using the NERSC cori system on the Intel Xeon Phi (KNL) partition.
Each node contains 68 cores, each capable of supporting up to 4 hardware threads (i.e., a maximum of 272 hardware threads per node).
For these tests, we assign 4 MPI tasks to each node, and 16 OpenMP threads per MPI process.
Each MPI task is assigned to a single grid, so our tests use between 64 and 13,824 MPI processes (i.e., between 1,024 and 221,184 total OpenMP threads).
For $64^3$ grids we discovered that using more than 16 OpenMP threads did not decrease the wallclock time due to a lack of work available per grid; in principle one could use larger grids, fewer MPI processes, and more threads per MPI process to obtain a flatter weak scaling curve, however the overall wallclock time would increase except for extremely large numbers of MPI processes (beyond the range we tested here).
Thus, the more accurate measure of weak scaling is to consider the number of MPI processes, since the scaling plot would look virtually identical for larger thread counts.
Note that the largest simulation used roughly 36\% of the entire computational system.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=3.0in]{./figs/MAESTRO_scaling1} \hspace{0.5em}
\includegraphics[width=3.0in]{./figs/MAESTRO_scaling2}
\caption{\label{fig:scaling} (Left) Weak scaling results for a spherical, full-star white dwarf calculation using the original MAESTRO code, MAESTROeX, and MAESTROeX with base state evolution disabled.  Shown is the average wallclock time per time step.
(Right) Weak scaling results showing the average wallclock time per time step spent in the cell-centered and nodal linear solvers within a full time step of the aforementioned simulations.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.75in]{./figs/wdconvect_256_maxT}  \hspace{0.5in}
\includegraphics[width=2.75in]{./figs/wdconvect_256_maxMach}
\caption{\label{fig:wdconvect_256_maxvar} (left) Peak temperature, $T_{\text{peak}}$, and (right) peak Mach number
         in a white dwarf until time of ignition at resolution of $256^3$ for three different MAESTROeX algorithms.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.5in]{./figs/reacting_bubble_amr} \hspace{2.5em}
\includegraphics[width=2.5in]{./figs/wdconvect_amr_3grid}
\caption{\label{fig:amr_grids} Initial grid structures with two levels of refinement.
         The red, green, and black lines represent grids of increasing refinement.
         (Left) Profile of $T - \bar{T}$ for a hot bubble in a white dwarf environment.
         (Right) Region of star where $\rho\ge 10^5 \text{ g cm}^{-3}$ in a full white dwarf star simulation. }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.5in]{./figs/reacting_bubble_result} \hspace{2.5em}
\includegraphics[width=2.5in]{./figs/reacting_bubble_amr_result}
\caption{\label{fig:bubble_results} Time-lapse cross-section of a hot bubble in a white dwarf environment at
         $t = 0$, 1.25, and 2.5 s for (left) single-level simulation, and
         (right) adaptive simulation at the same effective resolution.  The red, green, and black boxes indicate grids of increasing resolution}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsection{Performance and Scaling}\label{sec:scaling}
We perform weak scaling tests for simulations of convection preceding ignition in a spherical, full-star Chandrasekhar mass white dwarf. 
The simulation setup remains the same as reported in Section 3 of \cite{MAESTRO_AMR} and originally used in \cite{MAESTRO_convection}, and thus we emphasize that these scaling tests are performed using meaningful, scientific calculations.
Here, we perform simulations using $256^3, 512^3, 768^3, 1024^3, 1280^3$, and $1536^3$ grid cells on a spatially uniform grid (no AMR).
We divide each simulation into $64^3$ grids, so these simulations contain between 64 grids ($256^3$) and 13,824 grids ($1536^3$).
These simulations were performed using the NERSC cori system on the Intel Xeon Phi (KNL) partition.
Each node contains 68 cores, each capable of supporting up to 4 hardware threads (i.e., a maximum of 272 hardware threads per node).
For these tests, we assign 4 MPI tasks to each node, and 16 OpenMP threads per MPI process.
Each MPI task is assigned to a single grid, so our tests use between 64 and 13,824 MPI processes (i.e., between 1,024 and 221,184 total OpenMP threads).
For $64^3$ grids we discovered that using more than 16 OpenMP threads did not decrease the wallclock time due to a lack of work available per grid; in principle one could use larger grids, fewer MPI processes, and more threads per MPI process to obtain a flatter weak scaling curve, however the overall wallclock time would increase except for extremely large numbers of MPI processes (beyond the range we tested here).
Thus, the more accurate measure of weak scaling is to consider the number of MPI processes, since the scaling plot would look virtually identical for larger thread counts.
Note that the largest simulation used roughly 36\% of the entire computational system.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=3.25in]{./figs/MAESTRO_scaling1} \hspace{0.5em}
\includegraphics[width=3.25in]{./figs/MAESTRO_scaling2}
\caption{\label{fig:scaling} (Left) Weak scaling results for a spherical, full-star white dwarf calculation using the original MAESTRO code, MAESTROeX, and MAESTROeX with base state evolution disabled.  Shown is the average wallclock time per time step.
(Right) Weak scaling results showing the average wallclock time per time step spent in the cell-centered and nodal linear solvers within a full time step of the aforementioned simulations.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=3.25in]{./figs/wdconvect_256_maxT}  \hspace{0.5in}
\includegraphics[width=3.25in]{./figs/wdconvect_256_maxMach}
\caption{\label{fig:wdconvect_256_maxvar} (Left) Peak temperature, $T_{\text{peak}}$, and (Right) peak Mach number
         in a white dwarf until time of ignition at resolution of $256^3$ for three different MAESTROeX algorithms.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.5in]{./figs/reacting_bubble_amr} \hspace{2.5em}
\includegraphics[width=2.5in]{./figs/wdconvect_amr_3grid}
\caption{\label{fig:amr_grids} Initial grid structures with two levels of refinement.
         The red, green, and black lines represent grids of increasing refinement.
         (Left) Profile of $T - \bar{T}$ for a hot bubble in a white dwarf environment.
         (right) Region of star where $\rho\ge 10^5 \text{ g cm}^{-3}$ in a full white dwarf star simulation. }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.5in]{./figs/reacting_bubble_result} \hspace{2.5em}
\includegraphics[width=2.5in]{./figs/reacting_bubble_amr_result}
\caption{\label{fig:bubble_results} Time-lapse cross-section of a hot bubble in a white dwarf environment at
         $t = 0$, 1.25, and 2.5 s for (Left) single-level simulation, and
         (right) adaptive simulation at the same effective resolution.  The red, green, and black boxes indicate grids of increasing resolution}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
